Improving Haskell Theory Exploration

### 2015-12-04 TransferReport/background.tex
Fix some notation

\begin{figure}
  \begin{subfigure}[plus]{\textwidth}
    \begin{small}
      \underline{\texttt{plus}}
      \begin{verbatim}
Lam "a" (Lam "y" (Case (Var (Local "a"))
                       "b"
                       [Alt (DataAlt "Z") (Var (Local "y")) [],
                        Alt (DataAlt "S") (App (Var (Global "S"))
                                               (App (App (Var (Global "plus"))
                                                         (Var (Local  "x")))
                                                    (Var (Local "y"))))
                                          ["x"]]))
      \end{verbatim}
    \end{small}
  \end{subfigure}
  \begin{subfigure}[mult]{\textwidth}
    \begin{small}
      \underline{\texttt{mult}}
      \begin{verbatim}
Lam "a" (Lam "y" (Case (Var (Local "a"))
                       "b"
                       [Alt (DataAlt "Z") (Var (Global "Z")) [],
                        Alt (DataAlt "S") (App (App (Var (Global "plus"))
                                                    (Var (Local  "y")))
                                               (App (App (Var (Global "mult"))
                                                         (Var (Local  "x")))
                                                    (Var (Local  "y"))))
                                          ["x"]]))
      \end{verbatim}
    \end{small}
  \end{subfigure}
  \begin{subfigure}[odd]{\textwidth}
    \begin{small}
      \underline{\texttt{odd}}
      \begin{verbatim}
Lam "a" (Case (Var (Local "a"))
              "b"
              [Alt (DataAlt "Z") (Var (Global "False")) [],
               Alt (DataAlt "S") (App (Var (Global "even"))
                                      (Var (Local  "n")))
                                 ["n"]])
      \end{verbatim}
    \end{small}
  \end{subfigure}
  \begin{subfigure}[even]{\textwidth}
    \begin{small}
      \underline{\texttt{even}}
      \begin{verbatim}
Lam "a" (Case (Var (Local "a"))
              "b"
              [Alt (DataAlt "Z") (Var (Global "True")) [],
               Alt (DataAlt "S") (App (Var (Global "odd"))
                                      (Var (Local  "n")))
                                 ["n"]])
      \end{verbatim}
    \end{small}
  \end{subfigure}
  \caption{Translations of functions in figure \ref{fig:haskellexample} into the Core syntax of figure \ref{fig:coresyntax}. Notice the introduction of explicit $\lambda$ abstractions (\texttt{Lam}) and the use of \texttt{Case} to represent piecewise definitions. Fresh variables are chosen arbitrarily as \texttt{"a"}, \texttt{"b"}, etc.}
  \label{fig:coreexample}
\end{figure}

>>>>

\begin{figure}
  \begin{subfigure}[plus]{\textwidth}
    \begin{small}
      \underline{\texttt{plus}}
      \begin{verbatim}
Lam "a" (Lam "y" (Case (Var (Local "a"))
                       "b"
                       (Alt (DataAlt "Z") (Var (Local "y")))
                       (Alt (DataAlt "S") (App (Var (Global "S"))
                                               (App (App (Var (Global "plus"))
                                                         (Var (Local  "x")))
                                                    (Var (Local "y"))))
                                          "x")))
      \end{verbatim}
    \end{small}
  \end{subfigure}
  \begin{subfigure}[mult]{\textwidth}
    \begin{small}
      \underline{\texttt{mult}}
      \begin{verbatim}
Lam "a" (Lam "y" (Case (Var (Local "a"))
                       "b"
                       (Alt (DataAlt "Z") (Var (Global "Z")))
                       (Alt (DataAlt "S") (App (App (Var (Global "plus"))
                                                    (Var (Local  "y")))
                                               (App (App (Var (Global "mult"))
                                                         (Var (Local  "x")))
                                                    (Var (Local  "y"))))
                                          "x")))
      \end{verbatim}
    \end{small}
  \end{subfigure}
  \begin{subfigure}[odd]{\textwidth}
    \begin{small}
      \underline{\texttt{odd}}
      \begin{verbatim}
Lam "a" (Case (Var (Local "a"))
              "b"
              (Alt (DataAlt "Z") (Var (Global "False")))
              (Alt (DataAlt "S") (App (Var (Global "even"))
                                      (Var (Local  "n")))
                                 "n"))
      \end{verbatim}
    \end{small}
  \end{subfigure}
  \begin{subfigure}[even]{\textwidth}
    \begin{small}
      \underline{\texttt{even}}
      \begin{verbatim}
Lam "a" (Case (Var (Local "a"))
              "b"
              (Alt (DataAlt "Z") (Var (Global "True")))
              (Alt (DataAlt "S") (App (Var (Global "odd"))
                                      (Var (Local  "n")))
                                 "n"))
      \end{verbatim}
    \end{small}
  \end{subfigure}
  \caption{Translations of functions in figure \ref{fig:haskellexample} into the Core syntax of figure \ref{fig:coresyntax}. Notice the introduction of explicit $\lambda$ abstractions (\texttt{Lam}) and the use of \texttt{Case} to represent piecewise definitions. Fresh variables are chosen arbitrarily as \texttt{"a"}, \texttt{"b"}, etc.}
  \label{fig:coreexample}
\end{figure}

### 2015-12-04 TransferReport/contributions.tex
Fix some notation

Our approach will make use of the k-means algorithm described in \S \ref{sec:kmeans}, which considers the elements of a feature vector to be orthogonal. Hence we must ensure that similar expressions not only give rise to similar numerical values, but crucially that these values appear \emph{at the same position} in the feature vectors. Since expressions can be nested in different ways, simple traversals (breadth-first, depth-first, post-order, etc.) may cause features from equivalent sub-expressions to be mis-aligned. For example, if we read features in breadth-first order we might get the following feature vectors (padded to the same length with $0$):

\begin{small}
  \begin{equation*}
    \begin{array}{r@{}l@{}l@{}}
      X\ &=\ \CAlt\ (\CDataAlt\ \id{x})\ & (\vlocal{y}) \\
      Y\ &=\ \CAlt\ \CDefault\           & (\vlocal{y})
    \end{array}
  \end{equation*}

  \begin{equation*}
    \begin{array}{r@{}l@{}l@{}l@{}l@{}l@{}l@{}l}
      breadthFirst(X)\ &=\ (\feature{\CAlt},\ &\feature{\CDataAlt},\ &\feature{\CVar},\ &\feature{\id{x}},\ &\feature{\CLocal},\ &\feature{\id{y}} &) \\
      breadthFirst(Y)\ &=\ (\feature{\CAlt},\ &\feature{\CDefault},\ &\feature{\CVar},\ &\feature{\CLocal},\ &\feature{\id{y}},\ &0 &)
    \end{array}
  \end{equation*}
\end{small}

Here the common sub-expression $\vlocal{y}$ is misaligned, such that only $\frac{1}{6}$ features are guaranteed to match (others may match by coincidence, depending on $\feature{}$). These feature vectors might be deemed very dissimilar, despite the intuitive similarity of the expressions $X$ and $Y$ from which they derive.

If we were to align these features instead, by padding the third column rather than the sixth, then $\frac{4}{6}$ of the features would be guaranteed to match, making the similarity of the vectors more closely match our intuition and depend less on coincidence.

There are many approaches we could take to increase alignment. Our method, described below, is a variation of breadth-first traversal which pads each level of nesting to a fixed size. This doesn't guarantee alignment, but it does prevent misalignment from accumulating from one level to the next. In this example, our method (when padding each level to 2 features) would give the following feature vectors:

\begin{small}
  \begin{equation*}
    \begin{array}{r@{}l@{}l@{}l@{}l@{}l@{}l@{}l@{}l@{}l}
      featureVec(X)\ &=\ (\feature{\CAlt},\ &0,\ &\feature{\CDataAlt},\ &\feature{\CVar},\ &\feature{\id{x}},\  &\feature{\CLocal},\ &\feature{\id{y}},\ &0 &) \\
      featureVec(Y)\ &=\ (\feature{\CAlt},\ &0,\ &\feature{\CDefault},\ &\feature{\CVar},\ &\feature{\CLocal},\ &0,\                 &\feature{\id{y}},\ &0 &)
    \end{array}
  \end{equation*}
\end{small}

For this reason, we cannot Core expressions  we will associate first associate features (real numbers) with the syntax of figure \ref{fig:coresyntax}. To preserve the in two stages: first we construct \emph{rose trees} of features (real numbers), which maintain the nested structure of expressions shown in figure \ref{fig:coresyntax}. We then flatten these rose trees into feature vectors.

Rose trees are defined recursively: $T$ is a rose tree if $T = (f, T_1, \dots, T_{n_T})$, where $f \in \mathbb{R}$ and $T_i$ are rose trees. $T_i$ are the \emph{children of} $T$ and $f$ is the \emph{feature at} $T$. $n_T$ may be different for each child; trees where $n_T = 0$ are \emph{leaves}.

We turn Core expressions into rose trees by converting terminal symbols (such as \hs{Lam} or \hs{Rec}) into features; we represent this conversion using $\feature{}$. Non-terminal symbols (such as $expr$ and $id$) are converted recursively and become children. This is shown in figure \ref{fig:totree}.

\begin{figure}
  \begin{align*}
    toTree(e) &=
    \begin{cases}
      (\feature{\CVar}, toTree(e_1))                                 & \text{if $e = \CVar\ e_1$} \\
      (\feature{\CLit}, toTree(e_1))                                 & \text{if $e = \CLit\ e_1$} \\
      (\feature{\CApp}, toTree(e_1), toTree(e_2))                    & \text{if $e = \CApp\ e_1\ e_2$} \\
      (\feature{\CLam}, leaf(l_1), toTree(e_1))                      & \text{if $e = \CLam\ l_1\ e_1$} \\
      (\feature{\CLet}, toTree(e_1), toTree(e_2))                    & \text{if $e = \CLet\ e_1\ e_2$} \\
      (\feature{\CCase}, toTree(e_1), leaf(l_1), toTree(a_1), \dots) & \text{if $e = \CCase\ e_1\ l_1 [a_1, \dots]$} \\
      (\feature{\CType})                                            & \text{if $e = \CType$} \\
      (\feature{\CLocal}, leaf(l_1))                                & \text{if $e = \CLocal\ l_1$} \\
      (\feature{\CGlobal}, leaf(g_1))                               & \text{if $e = \CGlobal\ g_1$} \\
      (\feature{\CLitNum})                                          & \text{if $e = \CLitNum\ n_1$} \\
      (\feature{\CLitStr})                                          & \text{if $e = \CLitStr\ s_1$} \\
      (\feature{\CAlt}, toTree(e_1), toTree(e_2), leaf{l_1}, \dots)  & \text{if $e = \CAlt\ e_1 e_2 [l_1, \dots]$}  \\
      (\feature{\CDataAlt}, leaf(g_1))                              & \text{if $e = \CDataAlt\ g_1$}  \\
      (\feature{\CLitAlt}, toTree(e_1))                             & \text{if $e = \CLitAlt\ e_1$}  \\
      (\feature{\CDefault})                                         & \text{if $e = \CDefault$}  \\
      (\feature{\CNonRec}, toTree(e_1))                             & \text{if $e = \CNonRec\ e_1$}  \\
      (\feature{\CRec}, toTree(e_1), \dots)                         & \text{if $e = \CRec\ [e_1, \dots]$} \\
      (\feature{\CBind}, leaf(l_1), toTree(e_1))                    & \text{if $e = \CBind\ l_1 e_1$}
    \end{cases} \\
    leaf(x) &= (\feature{x})
  \end{align*}
  \caption{Recursively converting Core expressions of figure \ref{fig:coresyntax} to rose trees. List elements (indicated with $\dots$) are appended as children, rather than being wrapped in another tree.}
  \label{fig:totree}
\end{figure}

To flatten a rose tree we fetch the features from each ``level'', concatenating those from adjacent children:

@@

\begin{figure}
  \begin{small}
  \begin{align*}
    toTree(\hs{plus}) &= \\
      (\feature{\CLam},
       \begin{array}[t]{@{}l@{}}
         (\feature{\id{a}}), \\
         (\feature{\CLam},
          \begin{array}[t]{@{}l@{}}
            (\feature{\id{y}}), \\
            (\feature{\CCase},
             \begin{array}[t]{@{}l@{}}
               (\feature{\CVar}, (\feature{\CLocal}, (\feature{\id{a}}))), \\
               (\feature{\id{b}}), \\
               (\feature{\CAlt},
                \begin{array}[t]{@{}l@{}}
                  (\feature{\CDataAlt}, (\feature{\id{Z}})), \\
                  (\feature{\CVar}, (\feature{\CLocal}, (\feature{\id{y}})))),
                \end{array} \\
               (\feature{\CAlt},
                \begin{array}[t]{@{}l@{}}
                  (\feature{\CDataAlt}, (\feature{\id{S}})), \\
                  (\feature{\CApp},
                   \begin{array}[t]{@{}l@{}}
                     (\feature{\CVar}, (\feature{\CGlobal}, (\feature{\id{S}}))), \\
                     (\feature{\CApp},
                      \begin{array}[t]{@{}l@{}}
                        (\feature{\CApp},
                         \begin{array}[t]{@{}l@{}}
                           (\feature{\CVar}, (\feature{\CGlobal}, (\feature{\id{plus}}))), \\
                           (\feature{\CVar}, (\feature{\CLocal}, (\feature{\id{x}})))),
                         \end{array} \\
                      (\feature{\CVar}, (\feature{\CLocal}, (\feature{\id{y}}))))),
                      \end{array}
                   \end{array} \\
                  (\feature{\id{x}})))))
                \end{array}
             \end{array}
          \end{array}
       \end{array} \\
foo &= bar
  \end{align*}
  \end{small}
  \caption{}
  \label{fig:rosetreeexample}
\end{figure}

>>>>

Our approach will make use of the k-means algorithm described in \S \ref{sec:kmeans}, which considers the elements of a feature vector to be orthogonal. Hence we must ensure that similar expressions not only give rise to similar numerical values, but crucially that these values appear \emph{at the same position} in the feature vectors. Since different patterns of nesting can alter the ``shape'' of expressions, simple traversals (breadth-first, depth-first, post-order, etc.) may cause features from equivalent sub-expressions to be mis-aligned. For example, consider the following expressions, which represent pattern-match clauses with different patterns but the same body (\hs{\vlocal{y}}):

\begin{equation*}
  \begin{array}{r@{}l@{}l@{}}
    X\ &=\ \CAlt\ (\CDataAlt\ \id{C})\ & (\vlocal{y}) \\
    Y\ &=\ \CAlt\ \CDefault\           & (\vlocal{y})
  \end{array}
\end{equation*}

If we traverse these expressions in breadth-first order, converting each token to a feature using $\feature{}$ and padding to the same length with $0$, we would get the following feature vectors:

\begin{small}
  \begin{equation*}
    \begin{array}{r@{}l@{}l@{}l@{}l@{}l@{}l@{}l}
      breadthFirst(X)\ &=\ (\feature{\CAlt},\ &\feature{\CDataAlt},\ &\feature{\CVar},\ &\feature{\id{x}},\ &\feature{\CLocal},\ &\feature{\id{y}} &) \\
      breadthFirst(Y)\ &=\ (\feature{\CAlt},\ &\feature{\CDefault},\ &\feature{\CVar},\ &\feature{\CLocal},\ &\feature{\id{y}},\ &0 &)
    \end{array}
  \end{equation*}
\end{small}

Here the features corresponding to the common sub-expression $\CLocal\ \id{y}$ are misaligned, such that only $\frac{1}{3}$ of features are guaranteed to match (others may match by coincidence, depending on $\feature{}$). These feature vectors might be deemed very dissimilar during clustering, despite the intuitive similarity of the expressions $X$ and $Y$ from which they derive.

If we were to align these feature optimally, by padding the fourth column rather than the sixth, then $\frac{2}{3}$ of features would be guaranteed to match, making the similarity of the vectors more closely match our intuition and depend less on coincidence.

Our feature extraction method (described below) uses a variation of breadth-first traversal which pads each level of nesting to a fixed size. This doesn't guarantee alignment, but it does prevent mis-alignment from accumulating across different levels of nesting. For this example, our method (when padding each level to 2 features) would give the following feature vectors:

\begin{small}
  \begin{equation*}
    \begin{array}{r@{}l@{}l@{}l@{}l@{}l@{}l@{}l@{}l@{}l}
      featureVec_2(X)\ &=\ (\feature{\CAlt},\ &0,\ &\feature{\CDataAlt},\ &\feature{\CVar},\ &\feature{\id{x}},\  &\feature{\CLocal},\ &\feature{\id{y}},\ &0 &) \\
      featureVec_2(Y)\ &=\ (\feature{\CAlt},\ &0,\ &\feature{\CDefault},\ &\feature{\CVar},\ &\feature{\CLocal},\ &0,\                 &\feature{\id{y}},\ &0 &)
    \end{array}
  \end{equation*}
\end{small}

Here $\frac{1}{2}$ of the original 6 features align, which is more than $breadthFirst$ but not optimal. Both vectors have also been padded by an extra 2 zeros compared to $breadthFirst$; raising their alignment to $\frac{5}{8}$.

To achieve this we first transform the nested tokens of an expression into a \emph{rose tree} of features, using the $toTree$ function shown in figure \ref{fig:totree}. Rose trees are defined recursively: $T$ is a rose tree if $T = (f, T_1, \dots, T_{n_T})$, where $f \in \mathbb{R}$ and $T_i$ are rose trees. $T_i$ are the \emph{sub-trees} of $T$ and $f$ is the \emph{feature at} $T$. $n_T$ may differ for each (sub-) tree for each sub-tree; trees where $n_T = 0$ are \emph{leaves}. Rose trees for the Peano arithmetic functions of figure \ref{fig:coreexample} are given in figure \ref{fig:rosetreeexample}.

\begin{figure}
  \begin{align*}
    toTree(e) &=
    \begin{cases}
      (\feature{\CVar}, toTree(e_1))                                 & \text{if $e = \CVar\ e_1$} \\
      (\feature{\CLit}, toTree(e_1))                                 & \text{if $e = \CLit\ e_1$} \\
      (\feature{\CApp}, toTree(e_1), toTree(e_2))                    & \text{if $e = \CApp\ e_1\ e_2$} \\
      (\feature{\CLam}, leaf(l_1), toTree(e_1))                      & \text{if $e = \CLam\ l_1\ e_1$} \\
      (\feature{\CLet}, toTree(e_1), toTree(e_2))                    & \text{if $e = \CLet\ e_1\ e_2$} \\
      (\feature{\CCase}, toTree(e_1), leaf(l_1), toTree(a_1), \dots) & \text{if $e = \CCase\ e_1\ l_1 a_1 \dots$} \\
      (\feature{\CType})                                            & \text{if $e = \CType$} \\
      (\feature{\CLocal}, leaf(l_1))                                & \text{if $e = \CLocal\ l_1$} \\
      (\feature{\CGlobal}, leaf(g_1))                               & \text{if $e = \CGlobal\ g_1$} \\
      (\feature{\CLitNum})                                          & \text{if $e = \CLitNum\ n_1$} \\
      (\feature{\CLitStr})                                          & \text{if $e = \CLitStr\ s_1$} \\
      (\feature{\CAlt}, toTree(e_1), toTree(e_2), leaf{l_1}, \dots)  & \text{if $e = \CAlt\ e_1 e_2 l_1 \dots$}  \\
      (\feature{\CDataAlt}, leaf(g_1))                              & \text{if $e = \CDataAlt\ g_1$}  \\
      (\feature{\CLitAlt}, toTree(e_1))                             & \text{if $e = \CLitAlt\ e_1$}  \\
      (\feature{\CDefault})                                         & \text{if $e = \CDefault$}  \\
      (\feature{\CNonRec}, toTree(e_1))                             & \text{if $e = \CNonRec\ e_1$}  \\
      (\feature{\CRec}, toTree(e_1), \dots)                         & \text{if $e = \CRec\ e_1 \dots$} \\
      (\feature{\CBind}, leaf(l_1), toTree(e_1))                    & \text{if $e = \CBind\ l_1 e_1$}
    \end{cases} \\
    leaf(x) &= (\feature{x})
  \end{align*}
  \caption{Transforming Core expressions of figure \ref{fig:coresyntax} to rose trees. The recursive definition is mostly routine; each repeated element (shown as $\dots$) has an example to indicate their handling, e.g. for $\CAlt$ we use $leaf$ for each $l_i$. Also note that we ignore the value of literals, as it simplifies our later definition of $\feature{}$ and we conjecture that the effect on clustering real code is low.}
  \label{fig:totree}
\end{figure}

To flatten a rose tree we fetch the features from each ``level'', concatenating those from adjacent sub-trees:

@@

\begin{figure}
  \begin{small}
  \begin{align*}
    toTree(\hs{plus}) &= \\
      (\feature{\CLam},
       \begin{array}[t]{@{}l@{}}
         (\feature{\id{a}}), \\
         (\feature{\CLam},
          \begin{array}[t]{@{}l@{}}
            (\feature{\id{y}}), \\
            (\feature{\CCase},
             \begin{array}[t]{@{}l@{}}
               (\feature{\CVar}, (\feature{\CLocal}, (\feature{\id{a}}))), \\
               (\feature{\id{b}}), \\
               (\feature{\CAlt},
                \begin{array}[t]{@{}l@{}}
                  (\feature{\CDataAlt}, (\feature{\id{Z}})), \\
                  (\feature{\CVar}, (\feature{\CLocal}, (\feature{\id{y}})))),
                \end{array} \\
               (\feature{\CAlt},
                \begin{array}[t]{@{}l@{}}
                  (\feature{\CDataAlt}, (\feature{\id{S}})), \\
                  (\feature{\CApp},
                   \begin{array}[t]{@{}l@{}}
                     (\feature{\CVar}, (\feature{\CGlobal}, (\feature{\id{S}}))), \\
                     (\feature{\CApp},
                      \begin{array}[t]{@{}l@{}}
                        (\feature{\CApp},
                         \begin{array}[t]{@{}l@{}}
                           (\feature{\CVar}, (\feature{\CGlobal}, (\feature{\id{plus}}))), \\
                           (\feature{\CVar}, (\feature{\CLocal}, (\feature{\id{x}})))),
                         \end{array} \\
                      (\feature{\CVar}, (\feature{\CLocal}, (\feature{\id{y}}))))),
                      \end{array}
                   \end{array} \\
                  (\feature{\id{x}})))))
                \end{array}
             \end{array}
          \end{array}
       \end{array} \\
\iffalse
    toTree(\hs{mult}) &= \\
      (Lam "a" (Lam "y" (Case (Var (Local "a"))
                              "b"
                              [Alt (DataAlt "Z") (Var (Global "Z")) [],
                               Alt (DataAlt "S") (App (App (Var (Global "plus"))
                                                           (Var (Local  "y")))
                                                      (App (App (Var (Global "mult"))
                                                                (Var (Local  "x")))
                                                           (Var (Local  "y"))))
                                                 ["x"]])))

    toTree(\hs{odd}) &= \\
      (\feature{\CLam},
       \begin{array}[t]{@{}l@{}}
         (\feature{\id{a}}), \\
         (\feature{\CCase},
          \begin{array}[t]{@{}l@{}}
            (\feature{\CVar}, (\feature{\CLocal}, (\feature{\id{a}}))), \\
            (\feature{\id{b}}), \\
            (\feature{\CAlt},
             \begin{array}[t]{@{}l@{}}
               (\feature{\CDataAlt}, (\feature{\id{Z}})), \\
               (\feature{\CVar}, (\feature{\CGlobal}, (\feature{\id{False}})))),
             \end{array} \\
            (\feature{\CAlt},
             \begin{array}[t]{@{}l@{}}
               (\feature{\CDataAlt}, (\feature{\id{S}})), \\
               (\feature{\CApp},
                \begin{array}[t]{@{}l@{}}
                  (\feature{\CVar}, (\feature{\CGlobal}, (\feature{\id{even}}))), \\
                  (\feature{\CVar}, (\feature{\CLocal},  (\feature{\id{n}})))),
                \end{array} \\
               (\feature{\id{n}}))))
             \end{array}
          \end{array}
       \end{array}
\fi

    toTree(\hs{odd}) &= \\
      \begin{array}
        (\feature{\CLam}, &(\feature{\id{a}}),&                    &                      &                      &                           &                         \\
                          &(\feature{\CCase}, &(\feature{\CVar},   &(\feature{\CLocal},   &(\feature{\id{a}}))), &                           &                         \\
                          &                   &(\feature{\id{b}}), &                      &                      &                           &                         \\
                          &                   &(\feature{\CAlt},   &(\feature{\CDataAlt}, &(\feature{\id{Z}})),  &                           &                         \\
                          &                   &                    &(\feature{\CVar},     &(\feature{\CGlobal},  &(\feature{\id{False}})))), &                         \\
                          &                   &(\feature{\CAlt},   &(\feature{\CDataAlt}, &(\feature{\id{S}})),  &                           &                         \\
                          &                   &                    &(\feature{\CApp},     &(\feature{\CVar},     &(\feature{\CGlobal},       &(\feature{\id{even}}))), \\
                          &                   &                    &                      &(\feature{\CVar},     &(\feature{\CLocal},        &(\feature{\id{n}})))),   \\
                          &                   &                    &(\feature{\id{n}})))) &                      &                           &

       \end{array}
  \end{align*}
  \end{small}
  \caption{}
  \label{fig:rosetreeexample}
\end{figure}
